Miniproject - Algebraic Geometry

### 2021-12-09 Algebraic geometry/submission.tex
Added the degree formula for the Grassmanian
Added test for great new idea in alg geo

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{lemma}[definition]{Lemma}
\newtheorem{example}[definition]{Example}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{corollary}[definition]{Corollary}

@@

    This shows that the degree of $\Gr(2, 5)$ is indeed 5, as expected.

@@

\begin{lemma}
    Let $n \geq 4$ and
    \begin{equation*}
        J := \{ \{ A, B \} \ | \ A, B \in X, \ A \cap B = \emptyset \} \subseteq X^{(2)}
    \end{equation*}
    be a set, where
    \begin{equation*}
        X := \{ 1, ..., n \}^{(2)}
    \end{equation*}
    Then for $k \geq 3$ have
    \begin{equation*}
        |\{ A \in X^{(k)} \ | \ J \subseteq A \}| = 
    \end{equation*}
\end{lemma}
\begin{proof}
    Use induction on $n$.
    In the base case $n = 4$ have that
\end{proof}

\printbibliography
\end{document}

>>>>

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{lemma}[definition]{Lemma}
\newtheorem{example}[definition]{Example}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{corollary}[definition]{Corollary}
\newtheorem{theorem}[definition]{Theorem}

@@

    This shows that the degree of $\Gr(2, 5)$ is indeed 5, as expected from the degree formula mentioned in the lecture.
        \deg(\Gr(d, n)) = (d(n - d))! \frac {1! \cdot 2! \cdot ... \cdot (d - 1)!} {(n - d)! \cdot (n - d + 1)! \cdot ... \cdot (n - 1)!}
    which yields
        \deg(\Gr(2, 5)) = 6! \frac {1!} {3! \cdot 4!} = \frac {6 \cdot 5} {3!} = 5

@@

\paragraph{Another idea} Let
\begin{equation*}
    m_n(d) := |\{ x^\alpha \ \text{monomial} \ | \ \deg(x^\alpha) = d, \ x_{iv}x_{ju} \ \not| \ x^\alpha \}|
\end{equation*}
and
\begin{equation*}
    s_n(d) := |\{ x^\alpha \ \text{multilinear monomial} \ | \ \deg(x^\alpha) = d, \ x_{iv}x_{ju} \ \not| \ x^\alpha \}|
\end{equation*}
Then for sufficiently large $d$ have
\begin{equation*}
    m_n(d) = \sum_{i = 0}^n s_n(i) \left(\!\!{i \choose d - i}\!\!\right) = \sum_{i = 0}^n s_n(i) {d - 1 \choose i - 1}
\end{equation*}
Note now that we are only interested in the leading term of the polynomial, which is (more or less) given by the largest $i \leq n$ such that $s_n(i) \neq 0$.
So in fact, it suffices to find this.

For example, the dimension of $\Gr(2, n)$ is the size of the largest independent set $- 1$ in this strange graph I have been considering.

For example, I claim:
\begin{theorem}
    \begin{equation*}
        \dim(\Gr(2, n)) = 2n - 4
    \end{equation*}
\end{theorem}
\printbibliography
\end{document}
